Vision and Cognitive Systems Final Project

### 2020-06-30 Paper_Presentation/paper/paper.tex
metrics table

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Orb_matches/match3.png}}
\caption{Orb matches}
\label{fig_Orb_matches}
\end{figure}

@@

\section{Painting Replacement in the 3D Model}
The pipeline followed to accomplish this task is similar to the one explained before with a little difference. we start directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found. At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database. Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image.

@@

What is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification. this function in fact takes as input two images and project the first one on the plane of the second. if the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Labeling_precision_metrics/Precision_Labeling.png}}
\caption{labeling}
\label{fig_labeling}
\end{figure}

\begin{table}[htbp]
\caption{Metrics Table}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\section{Discussions}
Our approach is based on the assumption that input videos contain a relevant chromatic difference between paintings and background. when this assumption doesn’t occur, for example in the case of a wider shot comprising hallway too, otsu doesn’t manage to correctly differentiate paintings from the rest, which leads to worse performances.

\subsection{tested methods history}
At the beginning the idea was to use Canny, preceded by an initial noise removal obtained by bilateral filter, in order to find the edges on which to apply findContours opencv function. The results were not entirely satisfactory as the outlines often produced by canny did not accurately identify the picture. We therefore opted for a solution based on the thresholding of the RGB image, which as already explained above is followed by a refinement carried out at the hsv level. A method based only on hsv images was also tested, which revealed to be very performing in certain situations (in each frame there is a clear distinction between picture and background) but less stable than the previously exposed method.
It was then necessary to face the fact that each method, being based solely on image processing techniques, produced many false positives. The simplest way, according to which only bounding boxes containing a painting that had been matched on the database should have been shown, was discarded due to the limited database. many correctly identified paintings were in fact discarded because they were not present in the database. The solution adopted was to train an svm with the goal to classify what is a painting and what is not.

\section{References}
Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} C. Tomasi and R. Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat. No.98CH36271), Bombay, India, 1998, pp. 839-846, doi: 10.1109/ICCV.1998.710815..
\bibitem{b2} J. Zhang and J. Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp. 105-108, doi: 10.1109/CSSE.2008.206.
\bibitem{b3}Suzuki, S., and Be, K. (1985). Topological structural analysis of digitized binary images by border following. Computer Vision, Graphics, and Image Processing 30, 32–46. doi:10.1016/0734-189X(85)90016-7.
\bibitem{b4} 
\bibitem{b5} E. Rublee, V. Rabaud, K. Konolige and G. Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp. 2564-2571, doi: 10.1109/ICCV.2011.6126544.
\bibitem{b6}Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
\end{thebibliography}

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Orb_matches/match3.png}}
\caption{Orb matches}
\label{fig_Orb_matches}
\end{figure}
\bigskip

@@

\section{Painting Replacement in the 3D Model}
The pipeline followed to accomplish this task is similar to the one explained before with a little difference. It starts directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found. At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database. Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image.

@@

What is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification. This function in fact takes as input two images and project the first one on the plane of the second. If the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Labeling_precision_metrics/Precision_Labeling.png}}
\caption{Labeling}
\label{fig_labeling}
\end{figure}
\bigskip

\begin{table}[htbp]
\caption{Performances}
\begin{center}
\begin{tabular}{|c|c|}
\hline
\textbf{} & \textbf{\textit{Paintings}} \\
\hline
TP& 161\\
\hline
FP& 20\\
\hline
FN& 29\\
\hline
Average IoU& 0.860\\
\hline
Average Precision& 0.909\\
\hline
Average Recall& 0.906\\
\hline
Average F-Measure& 0.904\\
\hline
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\section{Discussions}
Our approach is based on the assumption that input videos contain a relevant chromatic difference between paintings and background. when this assumption doesn’t occur, for example in the case of a wider shot comprising hallway too, otsu doesn’t manage to correctly differentiate paintings from the rest, which leads to worse performances.
\subsection*{Tested methods history}
At the beginning the idea was to use Canny, preceded by an initial noise removal obtained by bilateral filter, in order to find the edges on which to apply findContours opencv function. The results were not entirely satisfactory as the outlines often produced by canny did not accurately identify the picture. We therefore opted for a solution based on the thresholding of the RGB image, which as already explained above is followed by a refinement carried out at the hsv level. A method based only on hsv images was also tested, which revealed to be very performing in certain situations (in each frame there is a clear distinction between picture and background) but less stable than the previously exposed method.\\
It was then necessary to face the fact that each method, being based solely on image processing techniques, produced many false positives. The simplest way, according to which only bounding boxes containing a painting that had been matched on the database should have been shown, was discarded due to the limited database. many correctly identified paintings were in fact discarded because they were not present in the database. The solution adopted was to train an svm with the goal to classify what is a painting and what is not.

\section*{}
\section*{}
\section*{}
\begin{thebibliography}{00}
\bibitem{b1} C. Tomasi and R. Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat. No.98CH36271), Bombay, India, 1998, pp. 839-846, doi: 10.1109/ICCV.1998.710815..
\bibitem{b2} J. Zhang and J. Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp. 105-108, doi: 10.1109/CSSE.2008.206.
\bibitem{b3}Suzuki, S., and Be, K. (1985). Topological structural analysis of digitized binary images by border following. Computer Vision, Graphics, and Image Processing 30, 32–46. doi:10.1016/0734-189X(85)90016-7.
\bibitem{b4} 
\bibitem{b5} E. Rublee, V. Rabaud, K. Konolige and G. Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp. 2564-2571, doi: 10.1109/ICCV.2011.6126544.
\bibitem{b6}Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
\end{thebibliography}
